Non-kissing complexes and tau-tilting \\ for gentle algebras

### 2018-07-13 firstPaper/corrections/replyToReferee.txt

(a) In Notation 1.50, the equalities were wrong and have been corrected.

(b) We have added some details (in a new Proposition 2.24) explaining why the 
    non-kissing facets are finite. In doing so, we had to slightly reorganise 
    Subsection 2.2.2 (new Lemma 2.23 was previously part of the proof of 
    Proposition (renumbered) 2.28).

* In the introduction, and in the introductory paragraphs of several sections
  the authors are sometimes quite abrupt and discuss notions that have not been
  introduced yet. For example examples this happens in
  - page 1, line 2: non-kissing paths
  - page 43: $\mathcal{L}_{nk}(\overline{Q})$
  Could this notions be introduces, at least vaguely, before using them?

  Reply: 
page 1: Modified to: The non-kissing complex is the simplicial complex of a compatibility relation, called non-kissing, on paths in a fixed shape of a grid.
page 43: We have added a reference to the definition.

@@

* proof of 2.21: ``follow'' is not really clear here

  Reply: Clarified.

* def 2.36: is any flip either increasing or decreasing?

  Reply: Yes. This has now been made explicit and we have added the definition of decreasing.

@@

* Example 3.44: It appears to me that the map, which is not explicit, is on the
  quotient of $Bic$

  Reply:

* pages 59,60,64,65,68,73 and probably more: the text goes outside the margin

  Reply: Fixed. We have checked that there are no text in the margin besides pictures and tables.

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
some more corrections

\begin{remark}
Assume that all strings of~$\bar Q$ are distinguishable, as happens for instance in grid and dissection quivers.
Then~$\omega_\bottom(\sigma)$ (resp.~$\omega_\top(\sigma)$) is obtained by adding a hook (resp.~a cohook) at each endpoint of~$\sigma$ while $\sigma_\bottom(\omega)$ (resp.~$\sigma_\top(\omega)$) is obtained by deleting a hook (resp.~a cohook) at each blossom of~$\omega$.
With the notations of Section~\ref{subsec:ARtranslationStringModules},
\[
\omega_\bottom(\sigma) = {}_h\sigma_h
\qquad\text{and}\qquad
\omega_\top(\sigma) = {}_c\sigma_c.
\]
In other words, when all strings of~$\bar Q$ are distinguishable, the bijections~$\omega_\bottom$ and~$\sigma_\bottom$ where already considered in Lemma~\ref{lem:bijections-STTC-NKC}.
As illustrated in \fref{fig:exmBijectionStringsWalks2}\,(right), the bijections of Lemma~\ref{lem:bijections-STTC-NKC} and Definition~\ref{def:bijectionWalksDistinguishableStrings} no longer coincide in general when not all strings are distinguishable.
\end{remark}

>>>>

\begin{remark}
Assume that all strings of~$\bar Q$ are distinguishable, as happens for instance in grid and dissection quivers.
Then~$\omega_\bottom(\sigma)$ (resp.~$\omega_\top(\sigma)$) is obtained by adding a hook (resp.~a cohook) at each endpoint of~$\sigma$ while $\sigma_\bottom(\omega)$ (resp.~$\sigma_\top(\omega)$) is obtained by deleting a hook (resp.~a cohook) at each blossom of~$\omega$.
With the notations of Section~\ref{subsec:ARtranslationStringModules},
\[
\omega_\bottom(\sigma) = {}_h\sigma_h
\qquad\text{and}\qquad
\omega_\top(\sigma) = {}_c\sigma_c.
\]
In other words, when all strings of~$\bar Q$ are distinguishable, the bijections~$\omega_\bottom$ and~$\sigma_\bottom$ where already considered in Lemma~\ref{lem:bijections-STTC-NKC}.
As illustrated in \fref{fig:exmBijectionStringsWalks2}\,(bottom), the bijections of Lemma~\ref{lem:bijections-STTC-NKC} and Definition~\ref{def:bijectionWalksDistinguishableStrings} no longer coincide in general when not all strings are distinguishable.
\end{remark}
